Stability and Chaos in Multi-Agent Reinforcement Learning

### 2020-10-08 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
minor mods

\begin{enumerate}
    \item A trivial result is that the game is everywhere convergent (i.e. regardless of the choice of $\Gamma, N, p$) for the cases of $\alpha$ = 0 and/or $\tau$ = 0.  We see that choosing these values would result in the right hand side of (\ref{eqn::Final}) yielding a value of zero which falls within the stable region.
    \item Convergence is rare. This is seen by the fact that the analytic result overestimates the region of instability. In fact, for all allowed choices of $\Gamma, \alpha, \tau$, the right hand side of (\ref{eqn::Final}) is negative, which violates the stability criterion. This implies that games, in general, will not converge.
    \item The likelihood of convergence decreases with increasing $\alpha$ and $\tau$, regardless of the choice of $N, p$. We can see this since the right hand side of (\ref{eqn::Final}) tends further away from zero (i.e. further from the region of stability).
    \item The choice of $\Gamma$ does not affect the stability of the game in the negatively-correlated regime. Therefore, the only dependent factors are $\alpha, \tau, N, p$. This is more easily interpreted from the heatmaps in Figure \ref{fig:theory}.
    \item The likelihood of convergence decreases as $p$ increases. We see this by noticing the weighting that the $(p-1)$ in the second term of (\ref{eqn::Final}) places. As $p$ increases, this term drives the system further from the stability boundary.

@@

We illustrate these implications in Figure \ref{fig:theory} which plots the value obtained by the right hand side of (\ref{eqn::Final}). In order to determine these values, we first had to solve (\ref{eqn::fixed_point}) for $q$ and $\chi$. We determine the $\xfixed$ which solves the expression inside the square brackets of (\ref{eqn::fixed_point}) using a Newton-Raphson root-finding approach and use the following expressions for $q, \chi$ to determine their value.

\begin{equation*}
    \begin{split}
        1 = \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z) exp(-\frac{z^2}{2}) dz \\ 
        q = \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z)^2 exp(-\frac{z^2}{2}) dz \\ 
        \chi = \frac{1}{q^{n/2}}\frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \frac{\partial \xfixed (z)}{\partial z} exp(-\frac{z^2}{2}) dz
    \end{split}
\end{equation*}

It should note that this method of finding $\xfixed$ yields only an approximate value and so the $q, \chi$ which are found are estimates of their true value.

We consider each of the implications (2)-(5) from the previous section
in turn, choosing to forego illustrating (1) as it can be seen immediately
from the expression. In those heatmaps where $\tau$ is held fixed
\textbf{denote them}, we choose $\tau = 0.05 $ and vary $\Gamma$ in
the range $[-1, 0]$ and $\alpha$ in the range $[0.01, 0.05]$. For
those in which $\alpha$ is held fixed, \textbf{denote them} we choose
$\alpha = 0.05$ and vary $\tau$ in the range $[0.01, 0.05]$.

>>>>

\begin{enumerate}
    \item A trivial result is that the game is everywhere convergent
      (i.e., regardless of the choice of $\Gamma$, $N$, $p$) for the cases
      of $\alpha = 0$ and/or $\tau = 0$.  We see that choosing these
      values would result in the right hand side of (\ref{eqn::Final})
      yielding a value of zero which falls within the stable region.

    \item Convergence is rare. This is seen by the fact that the
      analytic result overestimates the region of instability. In
      fact, for all allowed choices of $\Gamma$, $\alpha$, $\tau$, the
      right hand side of (\ref{eqn::Final}) is negative, which
      violates the stability criterion. This implies that games, in
      general, will not converge.

    \item The likelihood of convergence decreases with increasing
      $\alpha$ and $\tau$, regardless of the choice of $N$, $p$. We can
      see this since the right hand side of (\ref{eqn::Final}) tends
      further away from zero (i.e., further from the region of
      stability).

    \item The choice of $\Gamma$ does not affect the stability of the
      game in the negatively-correlated regime. Therefore, the only
      dependent factors are $\alpha$, $\tau$, $N$, $p$. This is more easily
      interpreted from the heatmaps in Figure~\ref{fig:theory} \fb{broken link}.

    \item The likelihood of convergence decreases as $p$ increases. We
      see this by noticing the weighting placed by $(p-1)$ in the
      second term of (\ref{eqn::Final}). As $p$ increases, this
      term drives the system further from the stability boundary.

@@

We illustrate these implications in Figure \ref{fig:theory} \fb{broken link} which
plots the value obtained by the right hand side of
(\ref{eqn::Final}). In order to determine these values, we first had
to solve (\ref{eqn::fixed_point}) for $q$ and $\chi$. We determine the
$\xfixed$ which solves the expression inside the square brackets of
(\ref{eqn::fixed_point}) using a Newton-Raphson root-finding approach
and use the following expressions for $q$, $\chi$ to determine their
value.
%
\begin{eqnarray*}
%    \begin{split}
        1 & = & \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z) exp(-\frac{z^2}{2}) dz \\ 
        q & = & \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z)^2 exp(-\frac{z^2}{2}) dz \\ 
        \chi & = & \frac{1}{q^{n/2}}\frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \frac{\partial \xfixed (z)}{\partial z} exp(-\frac{z^2}{2}) dz
%    \end{split}
\end{eqnarray*}

It should note that this method of finding $\xfixed$ yields only an
approximate value and so the $q$, $\chi$ which are found are estimates
of their true value.

We consider each of the implications (2)-(5)
%from the previous section
in turn, choosing to forego illustrating (1) as it can be seen
immediately from the expression \fb{add number}. In those heatmaps
where $\tau$ is held fixed \textbf{denote them}, we choose $\tau =
0.05 $ and vary $\Gamma$ in the range $[-1, 0]$ and $\alpha$ in the
range $[0.01, 0.05]$. For those in which $\alpha$ is held fixed,
\textbf{denote them} we choose $\alpha = 0.05$ and vary $\tau$ in the
range $[0.01, 0.05]$. \fb{I assume heatmaps are to be added.}
